---
title: "data prep - group 9"
author: 'Younchan Son, Silvan Michael Hofer, Ka Wing NG, Joanna '
date: "25. March 2022"
output:
  html_document:
    theme: united
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
#install.packages("quanteda")
#install.packages("quanteda.textplots")
#install.packages("quanteda.textmodels")

library(quanteda)
library(quanteda.textplots)
library(quanteda.textmodels)
library(glmnet)
library(writexl)
library(caret)
```



# Data preparation 
## 1. Load data
We have to be careful with the data since it is encoded in UTF-8. If we do not change the encoding, some symbols are wrongly recognized. 
```{r}
reviews <- read.csv("game_train.csv", encoding = "UTF-8")
games <- read.csv("games.csv", encoding = "UTF-8")
data.kaggle <- read.csv("game_test.csv", encoding = "UTF-8")
```

## 2. Combine data
We combine the reviews with data about the game. We notice that the dataset is relatively balanced so we do not have to over or undersample it. 
```{r}
data <- merge(reviews, games, by.x = "title", by.y = "title", all.x = T)
sum(data$user_suggestion)

data$doc_id <- 1:nrow(data)
train.id <- sample(1:nrow(data), 0.7*nrow(data))
test.id <- data$doc_id[!data$doc_id %in% train.id]
```
```{r, echo=FALSE}
rm(reviews, games)
```

## 3. Clean data

### 3.1 Remove Tags
The Start of the reviews had tags in them which provide further information. These are removed and put into a separate column. 
```{r}
data$is.early <- ifelse(grepl("Early Access Review", data$user_review), 1, 0)
data$user_review <- gsub("Early Access Review","", data$user_review)
data.kaggle$user_review <- gsub("Early Access Review","", data.kaggle$user_review)

data$received.free <- ifelse(grepl("Product received for free", data$user_review), 1, 0)
data$user_review <- gsub("Product received for free","", data$user_review)
data.kaggle$user_review <- gsub("Product received for free","", data.kaggle$user_review)


data$user_review <- gsub("Access Review", "", data$user_review) #unclear, just remove it
data.kaggle$user_review <- gsub("Access Review","", data.kaggle$user_review)
```

### 3.2 Create Document Term Matrix
Quanteda handily provides a function which does converts all characters to lower, removes punctuation, stopwords and URLs.
```{r}
library("corpus")
revcorpus <- corpus(x = data, 
                    docid_field ="doc_id", 
                    text_field = "user_review", 
                    meta = list("user_suggestion" = "user_suggestion")
                    )
revcorpus.kaggle <- corpus(x = data.kaggle, 
                           text_field = "user_review"
                    )
```
We want to remove certain stopwords. To make sure to not accidentally throw out wrong ones, we look at the standards stopwords. 
```{r}
stopwords("english")
```
We see some we want to keep and also add one to thow out. 
```{r}
custom.stopwords <- c(stopwords("english")[!stopwords("english") %in% c("no", "nor","not")], "░")

doc.term <- dfm(x = revcorpus, 
                tolower=TRUE, 
                stem=TRUE, 
                remove_punct = TRUE, 
                remove_url=TRUE, 
                verbose=FALSE, 
                remove = custom.stopwords)

doc.term.kaggle <- dfm(x = revcorpus.kaggle, 
                tolower=TRUE, 
                stem=TRUE, 
                remove_punct = TRUE, 
                remove_url=TRUE, 
                verbose=FALSE, 
                remove = custom.stopwords)

topfeatures(doc.term, 10)
```
We also trim the matrix
```{r}
doc.term <- dfm_trim(doc.term, min_docfreq=10, verbose=TRUE)

```

```{r}
textplot_wordcloud(doc.term, rotation=0, min_size=2, max_size=10, max_words=50)
```

###Split into train and test
```{r}
data.train <- dfm_subset(x = doc.term, docname_ %in% train.id)
data.test <- dfm_subset(x = doc.term, docname_ %in% test.id)
```

###Match same features
```{r}
data.test <- dfm_match(data.test, features = featnames(data.train))
data.kaggle <- dfm_match(doc.term.kaggle, features = featnames(data.train))

```

##Train naive bayes
```{r}
naive.bayes <- textmodel_nb(data.train, data.train$user_suggestion)
summary(naive.bayes)
```

##make prediction
```{r}
actual_class <- data.test$user_suggestion
predicted_class <- predict(naive.bayes, newdata = data.test)
tab_class <- table(actual_class, predicted_class)
tab_class
```
```{r}
confusionMatrix(tab_class, mode = "everything")
```


#make prediction for Kaggle
```{r}
prediction.kaggle <- data.frame(predict(naive.bayes, newdata = data.kaggle))


prediction.kaggle <- data.frame(matrix(ncol = 2, nrow = nrow(data.kaggle)))
prediction.kaggle[, 1] <- data.kaggle$review_id
prediction.kaggle[, 2] <- data.frame(predict(naive.bayes, newdata = data.kaggle))
names(prediction.kaggle)<- c("review_id", "user_suggestion")
```

#train gmlnet


```{r}
lasso <- cv.glmnet(x = data.train,
                   y = as.integer(data.train$user_suggestion == "1"),
                   alpha = 1,
                   nfold = 100,
                   family = "binomial")


prediction.gml <- predict(lasso, data.test, type = "response", s = lasso$lambda.min)
```


##make prediction
```{r}
actual_class <- data.test$user_suggestion
predicted_class <- as.integer(predict(lasso, newx = data.test, type = "class", s = lasso$lambda.min))
tab_class <- table(actual_class, predicted_class)
tab_class
confusionMatrix(tab_class, mode = "everything")
```
```{r}

```


#save prediction
```{r}
data.export <- convert(doc.term, to = "data.frame")
write.csv(data.export, file = "doc.term matrix")
write.csv(prediction.kaggle, file = "predictions.csv", row.names = F)
```


#Convert Data for decision tree & SVM
```{r}
library(caTools)
try.train = convert(data.train, to = "data.frame")
try.test = convert(data.test, to = "data.frame")
try.kaggle = convert(data.kaggle, to = "data.frame")

data_suggestion <- data.frame(data$user_suggestion, data$doc_id)
try.data <- merge(try.train, data_suggestion, by.x = "doc_id", by.y = "doc_id")
try.data <- merge(try.test, data_suggestion)


try_data$doc_id <- NULL
names(try_data)[1] <- 'user_suggestion'
```

```{r}
try_data$user_suggestion = factor(try_data$user_suggestion, levels = c(0, 1))

set.seed(123)
split1<- sample(c(rep(0, 0.7 * nrow(data)), rep(1, 0.3 * nrow(data))))
split1

train <- try_data[split1 == 0, ] 
test <- try_data[split1== 1, ]    

```


#Decision Tree Model
##1. Default Parameter
```{r}
library(rpart)
tree.model <- rpart(user_suggestion~., data = data.frame(train), method = 'class')
predict.tree <-predict(dt, data.frame(test), type = 'class')

#make confusion matrix
tree_confused <- confusionMatrix(as.factor(test$user_suggestion),predict.tree)
tree_confused

precision <- tree_confused$byClass['Pos Pred Value']
recall <- tree_confused$byClass['Sensitivity']

f_measure <- 2*((precision*recall)/(precision+recall))

f_measure
```

##2. tune parameter
###2.1 minsplit:10, minbucket:5, maxdepth:10
```{r}
accuracy_tune <- function(fit) {
    predict_unseen <- predict(fit, data.frame(test), type = 'class')
    table_mat <- table(test$suggestion, predict_unseen)
    accuracy_Test <- sum(diag(table_mat)) / sum(table_mat)
    accuracy_Test
}

control <- rpart.control(minsplit = 10,
    minbucket = round(5 / 3),
    maxdepth = 10,
    cp = 0.01)

tune_fit <- rpart(suggestion~., data = data.frame(train), method = 'class', control = control)

predict_1 <-predict(tune_fit, data.frame(test), type = 'class')

#make confusion matrix
tree_confused <- confusionMatrix(as.factor(test$suggestion),predict_1)
tree_confused

precision <- tree_confused$byClass['Pos Pred Value']
recall <- tree_confused$byClass['Sensitivity']

f_measure <- 2*((precision*recall)/(precision+recall))

f_measure
```

###2.2 minsplit:20, minbucket:100, maxdepth:30
```{r}
accuracy_tune <- function(fit) {
    predict_unseen <- predict(fit, data.frame(test), type = 'class')
    table_mat <- table(test$suggestion, predict_unseen)
    accuracy_Test <- sum(diag(table_mat)) / sum(table_mat)
    accuracy_Test
}

control <- rpart.control(minsplit = 20,
    minbucket = round(100 / 3),
    maxdepth = 30,
    cp = 0.01)

tune_fit <- rpart(suggestion~., data = data.frame(train), method = 'class', control = control)

predict_1 <-predict(tune_fit, data.frame(test), type = 'class')

#make confusion matrix
tree_confused <- confusionMatrix(as.factor(test$suggestion),predict_1)
tree_confused

precision <- tree_confused$byClass['Pos Pred Value']
recall <- tree_confused$byClass['Sensitivity']

f_measure <- 2*((precision*recall)/(precision+recall))

f_measure
```
The best result is 0.56731 only


#SVM Model
```{r}
library(e1071)
library(rpart)
library(class)

#Scale the data
train[-1] = scale(train[-1])
test[-1] = scale(test[-1])
```

```{r}
svm.model = svm(formula = user_suggestion ~ .,
                 data = train,
                 type = 'C-classification',
                 kernel = 'linear')
test_new <- test[-1]
predict.svm1 = predict(svm.model, data = test, type="class")
```

```{r}
#make confusion matrix
svm_confused <- confusionMatrix(as.factor(test$user_suggestion),predict.svm2)
svm_confused

precision <- svm_confused$byClass['Pos Pred Value']
recall <- svm_confused$byClass['Sensitivity']

f_measure <- 2*((precision*recall)/(precision+recall))

f_measure
```

#Tune Parameter for SVM
```{r}
#tune parameter
svm.model2 <- svm(user_suggestion ~ ., data = train, cost = 100, gamma = 1)
test_new <- test[-1]
predict.svm2 = predict(svm.model2, data = test, type="class")
```

```{r}
#make confusion matrix
svm2_confused <- confusionMatrix(as.factor(test$user_suggestion),predict.svm2)
svm2_confused

precision <- svm2_confused$byClass['Pos Pred Value']
recall <- svm2_confused$byClass['Sensitivity']

f_measure <- 2*((precision*recall)/(precision+recall))

f_measure

```

#Random Forest
```{r}
library(randomForest)
library(datasets)
library(caret)
```

```{r}
rf.model <- randomForest(user_suggestion~., data=train, proximity=TRUE) 
predict.rf <- predict(rf.model, data.frame(test))

```
```{r}
#make confusion matrix
rf_confused <- confusionMatrix(as.factor(test$user_suggestion),predict.rf)
rf_confused

precision <- rf_confused$byClass['Pos Pred Value']
recall <- rf_confused$byClass['Sensitivity']

f_measure <- 2*((precision*recall)/(precision+recall))

f_measure
```

