---
title: "data prep - group 9"
author: 'Younchan Son, Silvan Michael Hofer, Ka Wing NG, Joanna '
date: "25. March 2022"
output:
  html_document:
    theme: united
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
#install.packages("quanteda")
#install.packages("quanteda.textplots")

library(quanteda)
library(quanteda.textplots)
```



# Data preparation 
## 1. Load data
We have to be careful with the data since it is encoded in UTF-8. If we do not change the encoding, some symbols are wrongly recognized. 
```{r}
reviews <- read.csv("game_train.csv", encoding = "UTF-8")
games <- read.csv("games.csv", encoding = "UTF-8")

```

## 2. Combine data
We combine the reviews with data about the game. We notice that the dataset is relatively balanced so we do not have to over or undersample it. 
```{r}
data <- merge(reviews, games, by.x = "title", by.y = "title", all.x = T)
sum(data$user_suggestion)
```
```{r, echo=FALSE}
rm(reviews, games)
```

## 3. Clean data

### 3.1 Remove Tags
The Start of the reviews had tags in them which provide further information. These are removed and put into a separate column. 
```{r}
data$is.early <- ifelse(grepl("Early Access Review", data$user_review), 1, 0)
data$user_review <- gsub("Early Access Review","", data$user_review)

data$received.free <- ifelse(grepl("Product received for free", data$user_review), 1, 0)
data$user_review <- gsub("Product received for free","", data$user_review)

data$user_review <- gsub("Access Review", "", data$user_review) #unclear, just remove it
```

### 3.2 Create Document Term Matrix
Quanteda handily provides a function which does converts all characters to lower, removes punctuation, stopwords and URLs.
```{r}
revcorpus <- corpus(data$user_review)
```
We want to remove certain stopwords. To make sure to not accidentally throw out wrong ones, we look at the standards stopwords. 
```{r}
stopwords("english")
```
We see some we want to keep and als add one to thow out. 
```{r}
custom.stopwords <- c(stopwords("english")[!stopwords("english") %in% c("no", "nor","not")], "░")

doc.term <- dfm(x = revcorpus, 
                tolower=TRUE, 
                stem=TRUE, 
                remove_punct = TRUE, 
                remove_url=TRUE, 
                verbose=FALSE, 
                remove = custom.stopwords)


topfeatures(doc.term, 25)
```
We also trim the matrix
```{r}
doc.term <- dfm_trim(doc.term, min_docfreq=10, verbose=TRUE)
```

```{r}
textplot_wordcloud(doc.term, rotation=0, min_size=2, max_size=10, max_words=50)
```
```{r}
data.export <- convert(doc.term, to = "data.frame")
writexl::write_xlsx(data.export, file = "doc.term matrix.xlsx")
```

