---
title: "data prep - group 9"
author: 'Younchan Son, Silvan Michael Hofer, Ka Wing NG, Joanna '
date: "25. March 2022"
output:
  html_document:
    theme: united
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
#install.packages("quanteda")
#install.packages("quanteda.textplots")
#install.packages("quanteda.textmodels")

#install_version('randomForest', "4.6-14")
library(remotes)
library(quanteda)
library(quanteda.textplots)
library(quanteda.textmodels)
library(glmnet)
library(randomForest)
library(writexl)
library(caret)
```



# Data preparation 
## 1. Load data
We have to be careful with the data since it is encoded in UTF-8. If we do not change the encoding, some symbols are wrongly recognized. 
```{r}
reviews <- read.csv("game_train.csv", encoding = "UTF-8")
games <- read.csv("games.csv", encoding = "UTF-8")
data.kaggle <- read.csv("game_test.csv", encoding = "UTF-8")
```

## 2. Combine data
We combine the reviews with data about the game. We notice that the dataset is relatively balanced so we do not have to over or undersample it. 
```{r}
data <- merge(reviews, games, by.x = "title", by.y = "title", all.x = T)
sum(data$user_suggestion)

data$doc_id <- 1:nrow(data)
train.id <- sample(1:nrow(data), 0.7*nrow(data))
test.id <- data$doc_id[!data$doc_id %in% train.id]
```
```{r, echo=FALSE}
rm(reviews, games)
```

## 3. Clean data

### 3.1 Remove Tags
The Start of the reviews had tags in them which provide further information. These are removed and put into a separate column. 
```{r}
data$is.early <- ifelse(grepl("Early Access Review", data$user_review), 1, 0)
data$user_review <- gsub("Early Access Review","", data$user_review)
data.kaggle$user_review <- gsub("Early Access Review","", data.kaggle$user_review)

data$received.free <- ifelse(grepl("Product received for free", data$user_review), 1, 0)
data$user_review <- gsub("Product received for free","", data$user_review)
data.kaggle$user_review <- gsub("Product received for free","", data.kaggle$user_review)


data$user_review <- gsub("Access Review", "", data$user_review) #unclear, just remove it
data.kaggle$user_review <- gsub("Access Review","", data.kaggle$user_review)
```

### 3.2 Create Document Term Matrix
Quanteda handily provides a function which does converts all characters to lower, removes punctuation, stopwords and URLs.
```{r}
revcorpus <- corpus(x = data, 
                    docid_field ="doc_id", 
                    text_field = "user_review", 
                    meta = list("user_suggestion" = "user_suggestion")
                    )
revcorpus.kaggle <- corpus(x = data.kaggle, 
                           text_field = "user_review"
                    )
```
We want to remove certain stopwords. To make sure to not accidentally throw out wrong ones, we look at the standards stopwords. 
```{r}
stopwords("english")
```
We see some we want to keep and als add one to thow out. 
```{r}
custom.stopwords <- c(stopwords("english")[!stopwords("english") %in% c("no", "nor","not")], "░")

doc.term <- dfm(x = revcorpus, 
                tolower=TRUE, 
                stem=TRUE, 
                remove_punct = TRUE, 
                remove_url=TRUE, 
                verbose=FALSE, 
                remove = custom.stopwords)

doc.term.kaggle <- dfm(x = revcorpus.kaggle, 
                tolower=TRUE, 
                stem=TRUE, 
                remove_punct = TRUE, 
                remove_url=TRUE, 
                verbose=FALSE, 
                remove = custom.stopwords)

topfeatures(doc.term, 10)
```
We also trim the matrix
```{r}
doc.term <- dfm_trim(doc.term, min_docfreq=10, verbose=TRUE)

```

```{r}
textplot_wordcloud(doc.term, rotation=0, min_size=2, max_size=10, max_words=50)
```

###Split into train and test
```{r}
data.train <- dfm_subset(x = doc.term, docname_ %in% train.id)
data.test <- dfm_subset(x = doc.term, docname_ %in% test.id)
```

###Match same features
```{r}
data.test <- dfm_match(data.test, features = featnames(data.train))
data.kaggle <- dfm_match(doc.term.kaggle, features = featnames(data.train))

```

##Train naive bayes
```{r}
naive.bayes <- textmodel_nb(data.train, data.train$user_suggestion)
summary(naive.bayes)
```

##make prediction
```{r}
actual_class <- data.test$user_suggestion
predicted_class <- predict(naive.bayes, newdata = data.test)
tab_class <- table(actual_class, predicted_class)
tab_class
```
```{r}
confusionMatrix(tab_class, mode = "everything")
```


#make prediction for Kaggle
```{r}
prediction.kaggle <- data.frame(predict(naive.bayes, newdata = data.kaggle))


prediction.kaggle <- data.frame(matrix(ncol = 2, nrow = nrow(data.kaggle)))
prediction.kaggle[, 1] <- data.kaggle$review_id
prediction.kaggle[, 2] <- data.frame(predict(naive.bayes, newdata = data.kaggle))
names(prediction.kaggle)<- c("review_id", "user_suggestion")
```

#train gmlnet


```{r}
lasso <- cv.glmnet(x = data.train,
                   y = as.integer(data.train$user_suggestion == "1"),
                   alpha = 1,
                   nfold = 100,
                   family = "binomial")


prediction.gml <- predict(lasso, data.test, type = "response", s = lasso$lambda.min)
```


##make prediction
```{r}
actual_class <- data.test$user_suggestion
predicted_class <- as.integer(predict(lasso, newx = data.test, type = "class", s = lasso$lambda.min))
tab_class <- table(actual_class, predicted_class)
tab_class
confusionMatrix(tab_class, mode = "everything")
```



#train random Forest

```{r}
data.export <- na.omit(data.export)
data.export <- data.export[, -1]
forrest <- rfcv(trainx = data.export, trainy = as.integer(data.train$user_suggestion))
```



#save prediction
```{r}
data.export <- convert(doc.term, to = "data.frame")
write.csv(data.export, file = "doc.term matrix")
write.csv(prediction.kaggle, file = "predictions.csv", row.names = F)
```




